### 2019-08-30 manuscript/methods.tex
All legends fixed

Using the marginal likelihood values, we calculated Bayes factors to answer five key biological and methodological questions:
\begin{enumerate}
\item Are diversification patterns only determined by hidden states and not the traits of interest?---Comparison of character independent models against hidden state (\cref{table:bayesfactors,table:M11M15,supptable:M6M10,supptable:M16M20,supptable:M21M25}).
\item Are hidden states necessary to explain diversification rate heterogeneity?---Comparison of simple models against hidden state models (\cref{supptable:testaddhidden}).
\item Does a second focal trait add information about the diversification process?---Comparison of lumped models against IC/CD/CP models (\cref{figure:lumped,table:lumped,suppfigure:lumpedDP,suppfigure:lumpedIC}).
\item Are conclusions robust to assumptions about hidden state transitions?---Comparison amongst hidden states models with equal hidden rates and asymmetrical rates (\cref{supptable:asymmetry,suppfigure:asymmetric}).
\item Is there evidence for diploidization?---Comparison amongst models with and without diploidization (\cref{supptable:testdiploidization,suppfigure:alldip}).
\end{enumerate}

Each model comparison is reported with a Bayes factor on the natural log scale: the comparison between models $M_0$ and $M_1$ is $K=ln(BF(M_1,\ M_0)) = \ln[ P(\mathbf{X} | M_1) - P(\mathbf{X} | M_0)]$.
There is `strong evidence' for $M_1$ when this value is more than 10, moderate support if the value is more than 1, and no evidence if the value is between -1 and 1.
If the value of $K$ is negative the evidence goes towards $M_0$ \citep{kass1995}.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{states.pdf}
\caption{
Character states used in the models.
(A) Each species retained on the phylogeny belonged to one of five possible categories, depending on whether ploidy and/or breeding system were known. 
Number of species in each category is indicated; for example, 70 species are self-compatible with unknown ploidy.
Character state abbreviations are: $I$ for self-incompatible, $C$ for self-compatible, $D$ for diploid, $P$ for polyploid, $?$ for unknown.
Because polyploidization breaks this form of self-incompatibility, self-incompatible species with unobserved ploidy ($I?$) are taken to be diploid ($ID$), and polyploid species with unobserved breeding system ($?P$) are taken to be SC ($CP$).
(B) Category groupings into states for each model class.
In the ploidy-only models (M1- M10), states are coded as $D$ \& $P$ when uncertain/consistent with either state; in the breeding system-only models (M11-M15) such states are coded as $C$; in the ploidy and breeding system models (M16-M29), they are coded as $CD$ \& $CP$.
In the hidden-trait models, all species could take on either of two `hidden' character states. %IM: #33 
Two species, \emph{Lycium californicum} and \emph{Solanum bulbocastanum}, are simultaneously $ID$ and $CP$, and by adding them the sample adds to the total of 651 taxa used for analyses.
}
\label{figure:stateclassifications}
\end{figure}

\begin{suppfigure}
    \caption{ All models.  [This figure is provided as a separate, large-format page.] }
    \label{fig:allmodels}
\end{suppfigure}

@@

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M2    & M3     & M4    & M5     & Evidence                                                                                     \\ \hline
M1. D/P              & -1283.76                                                          & 59.90 & 49.23  & 60.48 & 58.82  & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M1\end{tabular}            \\ \hline
\textbf{M2. CID D/P} & \textbf{-1223.86}                                                 &       & -10.66 & 0.579 & -1.079 & \begin{tabular}[c]{@{}l@{}}Strong preference for \\ M2 over M1\end{tabular}              \\ \hline
M3. D/P+A/B          & -1234.52                                                          &       &        & 11.24 & 9.58   & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}   \\ \hline
\textbf{M4. D/P+A/B asym}     & \textbf{-1223.28}                                                          &       &        &       & -1.658 & \begin{tabular}[c]{@{}l@{}}Moderate evidence for\\ only asymmetric hidden rates\end{tabular} \\\hline
M5. D/P+A/B all asym & -1224.93                                                          &       &        &       &        &          \\ \hline                                                                                   
\end{tabular}
\caption{Bayes factors of  ploidy-only models without diplodization. Numbers greater that 1 mean moderate support relative to the model in the row label.  Conventional threshold for `strong' support is 10. The best models are written in bold. }
\label{table:bayesfactors}
\end{table}

% B: M111->M11
\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                      & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M12   & M13   & M14   & M15   & Evidence                                                                                       \\ \hline
M11. I/C                   & -1309.07                                                          & 41.13 & 38.59 & 61.34 & 61.40 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M11\end{tabular}            \\ \hline
M12. CID I/C               & -1267.93                                                          &       & -2.53 & 20.21 & 20.37 & \begin{tabular}[c]{@{}l@{}}Models with asymmetric rates\\ are preferred over  M12\end{tabular} \\ \hline
M13. I/C+A/B               & -1270.47                                                          &       &       & 22.75 & 22.80 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}   \\ \hline
\textbf{M14. I/C+A/B asym} & \textbf{-1247.72}                                                 &       &       &       & 0.05 & No evidence                                                                                    \\ \hline
\textbf{M15. I/C+A/B all asym }     & \textbf{ -1247.66}                                                          &       &       &       &       &       \\ \hline                                                                                        
\end{tabular}
\caption{Bayes factors of breeding system-only models. Results indicate that the HiSSE models with asymmetric rates (M14, M15) are strongly preferred over every other model.}
\label{table:M11M15}
\end{table}

@@

\begin{table}[]
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|c|c|c|c|}
\hline
Model                       & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & Comparison  & K=ln(BF($M_{i}$,$M_{ii}$)) & \begin{tabular}[c]{@{}l@{}}Preferred\\ Model (Evidence)\end{tabular} \\ \hline
M26. Lumped D/P             & -1463.22                                                          & M26 vs. M16 & 4.10            & M16 (Moderate)                                                       \\
\textbf{M16. ID/CD/CP}      & \textbf{-1459.11}                                                 &             &                 &                                                                      \\ \hline
M27. Lumped D/P+A/B         & -1417.67                                                          & M27 vs. M23 & 3.678           & M23 (Moderate)                                                       \\
\textbf{M23. ID/CD/CP +A/B} & \textbf{-1414.00}                                                 &             &                 &                                                                      \\ \hline
M28. Lumped I/C             & -1458.41                                                          & M28 vs. M16 & -0.69           & No evidence                                                          \\
\textbf{M16. ID/CD/CP}      & \textbf{-1459.11}                                                 &             &                 &                                                                      \\ \hline
M29. Lumped I/C+ A/B        & -1416.60                                                          & M29 vs. M23 & 2.60            & M23 (Moderate)                                                       \\
\textbf{M23. IC/CD/CP+A/B}  & \textbf{-1414.00}                                                 &             &                 &                                                                      \\ \hline
\end{tabular}
\caption{Test for adding a focal trait to a binary state model via Bayes factors. Three-state models are moderately preferred over two-state models. The evidence is stronger towards the inclusion of breeding systems in ploidy models (M26, M27) than the inclusion of ploidy in breeding system models (M29, M29)}
\label{table:lumped}
\end{table}

\begin{figure}
\includegraphics[width=\textwidth]{alldiversificationasymhidden.pdf} 
\caption{Net diversification rates for SSE models of focal traits with or without hidden state. 
Each panel contains a graphical summary of estimated model parameters and displays posterior distributions for net diversification estimates.}
\label{figure:netdivall}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{lumped.pdf} %lumped.pdf
\caption{Comparing two and three state models is possible via lumpable models (M26, M28). These models used the same classifications as the three-state model M16 which allow for comparisons via Bayes Factors as shown in \cref{table:lumped}.}  
\label{figure:lumped}
\end{figure}

@@

\begin{supptable}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                           & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M7    & M8     & M9    & M10   & Evidence                                                                                     \\ \hline
M6. D/P+$\delta$                & -1268.83                                                          & 55.41 & 42.78  & 53.37 & 52.85 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M6\end{tabular}            \\ \hline
\textbf{M7. CID D/P+$\delta$}   & \textbf{-1212.42}                                                 &       & -12.62 & -2.04 & -2.04 & \begin{tabular}[c]{@{}l@{}}Model M7 moderately\\ preferred over M9 and M10\end{tabular}      \\ \hline
M8. D/P+A/B $\delta$            & -1214.46                                                          &       &        & 10.58 & 10.07 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular} \\ \hline
M9. D/P+A/B +$\delta$ asym      & -1214.46                                                          &       &        &       & -0.51 & No evidence                                                                                  \\ \hline
M10. D/P+A/B +$\delta$ all asym & -1214.97                                                          &       &        &       &       &         \\ \hline                                                                                    
\end{tabular}
\caption{Bayes factors of  ploidy-only models with diplodization. Results indicate that a character independent model (M6) is strongly preferred over BiSSE (M1)  model. M6 is moderately preferred over any of the HiSSE models with asymmetric hidden rates (M9, M10).}
\label{supptable:M6M10}
\end{supptable}

\begin{supptable}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                            & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M18   & M19   & M20   & Evidence                                                                                                   \\ \hline
M16. ID/CP/CD                    & -1459.11                                                          & 45.11 & 65.91 & 63.98 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M16\end{tabular}                         \\ \hline
M17. CID ID/CP/CD                & *                                                                 &       &       &       &                                                                                                            \\
M18. ID/CP/CD+A/B                & -1414                                                             &       & 20.79 & 18.87 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}               \\ \hline
\textbf{M19. ID/CP/CD +A/B asym} & \textbf{-1393.20}                                                 &       &       & -1.92 & \begin{tabular}[c]{@{}l@{}}Asymmetric hidden rates moderately\\ preferred over all asymmetric\end{tabular} \\ \hline
M20. ID/CP/CD +A/B all asym      & -1393.12                                                          &       &       &       &   \\ \hline                                                                                                        
\end{tabular}
\caption{Bayes factors of ploidy and breeding system without diploidization. Results indicate that the MuHiSSE model with asymmetric hidden rates (17) is  strongly preferred over M16 and M18 and moderately preferred over the MuHiSSe with all rates asymetric (M20). *Marginal log-likelihood for M17 could not be calculated within allotted computer time.}
\label{supptable:M16M20}
\end{supptable}

\begin{supptable}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                                 & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M22   & M23    & M24   & M25   & Evidence                                                                                         \\ \hline
M21. ID/CP/CD+$\delta$                & -1454.68                                                          & 55.48 & 46.031 & 67.94 & 65.15 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M21\end{tabular}               \\ \hline
M22. CID ID/CP/CD+$\delta$            & -1399.201                                                         &       & -9.452 & 12.45 & 9.675 & \begin{tabular}[c]{@{}l@{}}Model M24 strongly preferred \\ over M22\end{tabular}                 \\ \hline
M23. ID/CP/CD+A/B $\delta$            & -1408.65                                                          &       &        & 21.91 & 19.12 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}     \\ \hline
\textbf{M24. ID/CP/CD +$\delta$ asym} & \textbf{-1386.74}                                                 &       &        &       & -2.78 & \begin{tabular}[c]{@{}l@{}}Asymmetric hidden rates \\ preferred over all asymmetric\end{tabular} \\ \hline
M25. ID/CP/CD +$\delta$ all asym      & -1389.52                                                          &       &        &       &       &                      \\ \hline                                                                           
\end{tabular}
\caption{Bayes factors of ploidy and breeding system with diploidization. Results indicate that the MuHiSSE model with asymmetric hidden rates (M24) is  strongly preferred over M21-M23 and moderately preferred over the MuHiSSe with all rates asymmetric (M25).}
\label{supptable:M21M25}
\end{supptable}

\begin{supptable}
\addtolength{\tabcolsep}{-5pt}
\begin{tabular}{|l|c|c|c|c|}
\hline
Model                                    & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & Comparison  & K=log(BF(M1,M2) & \begin{tabular}[c]{@{}l@{}}Preferred\\ Model (Evidence)\end{tabular} \\ \hline
M1. D/P                                  & -1238.76                                                          & M1 vs. M4   & 60.47           & M4 (Strong)                                                          \\
\textbf{M4. D/P+A/B asym}                & \textbf{-1223.28}                                                &             &                 &                                                                      \\ \hline
M11. I/C                                 & -1309.07                                                          & M11 vs. M14 & 61.35           & M14 (Strong)                                                         \\
\textbf{M14. I/C+A/B asym}               & \textbf{-1247.72}                                                 &             &                 &                                                                      \\ \hline
M16. ID/CD/CP                            & -1459.11                                                          & M16 vs. M19 & 65.90           & M19 (Strong)                                                         \\
\textbf{M19. ID/CD/CP+A/B asym}          & \textbf{-1393.20}                                                &             &                 &                                                                      \\ \hline
M6. D/P+$\delta$                         & -1283.76                                                          & M6 vs. M9   & 69.3            & M9 (Strong)                                                          \\
\textbf{M9. D/P+A/B+$\delta$ asym}       & \textbf{-1214.46}                                                 &             &                 &                                                                      \\ \hline
M21. IC/CD/CP+$\delta$                   & -1454.68                                                          & M21 vs. M24 & 68.48           & M24 (Strong)                                                         \\
\textbf{M24. IC/CD/CP+A/B+$\delta$ asym} & \textbf{-1386.20}                                                 &             &                 &                                                                      \\ \hline
\end{tabular}
\caption{Test for addition of hidden states in models via Bayes factors. Models with hidden states are strongly preferred over simpler models}
\label{supptable:testaddhidden}
\end{supptable}

\begin{supptable}
\addtolength{\tabcolsep}{-5pt}
\begin{tabular}{|l|c|c|c|l|}
\hline
Model                                    & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & Comparison  & K=log(BF(M1,M2) & \begin{tabular}[c]{@{}l@{}}Preferred\\ Model (Evidence)\end{tabular} \\ \hline
M3. D/P+A/B                                 & -1234.52                     &    M3 vs. M4                 & 11.239                  & M4 (Strong)   \\
\textbf{M4. D/P+ A/B asym}            & -1223.28                     &   M4 vs. M5              & -1.658                  & M4 (Moderate)   \\
M5. D/P+A/B all asym                 & -1224.93                     &                     &                         &                         \\ \hline
M13. I/C+ A/B                                & -1270.47                     &   M13 vs. M14                  & 22.75                   & M14 (Strong)   \\
\textbf{M14. I/C+ A/B asym}            & \textbf{-1247.72}            & M14 vs. M15         & {0.05}           & No evidence             \\
M15. I/C+ A/B all asym               & -1247.67                     &                     &                         &                         \\ \hline
M18. IC/CD/CP+A/B                            & -1414.00                     &     M18 vs. M19                & 20.79                   & M19 (Strong)    \\
\textbf{M19. IC/CD/CP+ A/B asym}       & \textbf{-1393.21}            & M19 vs. M20          & {-1.919}         & M19 (Moderate)   \\
M20. IC/CD/CP+ A/B all asym           & -1395.129                    &                     &                         &                         \\ \hline
M8. D/P +A/B+$\delta$                          & -1225.05                     &  M8 vs. M9                   & 10.58                   & M9 (Strong)    \\
\textbf{M9. D/P+ A/B+ $\delta$ asym}      & \textbf{-1214.46}                     &    M9 vs. M10                 & -0.52                   & M10 (Moderate) \\
M10. D/P+A/B+$\delta$ all asym        & -1214.98                     &                    &                         &                         \\ \hline
M23. IC/CD/DP+A/B+$\delta$                 & -1408.65                     &     M23 vs M24                & 21.91                   & M24(Strong)     \\
\textbf{M24. IC/CD/DP+A/B+$\delta$ asym} & \textbf{-1386.74}                     &   M24 vs M25              & -2.78                   & M24 (Moderate) \\
M25. IC/CD/DP+A/B+ $\delta$ all asym     & -1389.52                     &                     &                         &                         \\ \hline
\end{tabular}
\caption{Test for symmetry of the hidden trait transition rates via Bayes factors. For all models, asymmetric transition rates between hidden trait states are preferred over models with equal rates. Adding more complexity by assuming asymmetry in all rates within both hidden states does not improve models.} %FIXME/CHECK
\label{supptable:asymmetry}
\end{supptable}

\begin{supptable}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|c|c|c|c|}
\hline
Model                                    & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & Comparison  & K=log(BF(M1,M2) & \begin{tabular}[c]{@{}l@{}}Preferred\\ Model (Evidence)\end{tabular} \\ \hline
M1. D/P                                  & -1238.76                                                          & M1 vs. M6   & 65.92           & M6 (Strong)                                                          \\
\textbf{M6. D/P+$\delta$}                & \textbf{-1267.84}                                                 &             &                 &                                                                      \\ \hline
M4. D/P+A/B asym                         & -1223.28                                                          & M4 vs. M9   & 8.81            & M9 (Moderate)                                                        \\
\textbf{M9. D/P+A/B+$\delta$ asym}       & \textbf{-1214.46}                                                 &             &                 &                                                                      \\ \hline
M16. ID/CD/CP                            & -1459.11                                                          & M16 vs. M21 & 4.41            & M21 (Moderate)                                                       \\
\textbf{M21. ID/CD/CP+$\delta$}          & \textbf{-1454.68}                                                 &             &                 &                                                                      \\ \hline
M19. IC/CD/CP +A/B asym                       & -1393.20                                                          & M19 vs. M24 & 6.46            & M24 (Moderate)                                                       \\
\textbf{M24. IC/CD/CP+A/B+$\delta$ asym} & \textbf{-1386.20}                                                 &             &                 &                                                                      \\ \hline
\end{tabular}
\caption{Test for inclusion of a diploidization rate via Bayes factors. Models with diploidization are moderately preferred over models that do not include a diploidization rate}
\label{supptable:testdiploidization}
\end{supptable}

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseDPnodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the M1, D/P ploidy model.} % XXX
\label{suppfigure:DPnodip}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseDPnodipasymposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the M4, D/P+A/B asym model.} % XXX
\label{suppfigure:DPnodipAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the M11, I/C breeding system model.} % XXX
\label{suppfigure:IC}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseSIasymposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the M14, I/C+A/B asym model.} % XXX
\label{suppfigure:ICAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{musseDPSInodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the  M16, ID/CD/CP model.} % XXX
\label{suppfigure:IDCDCPnodip}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{muhissenodipasymposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the M19, ID/CD/CP+A/B asym model.} % XXX
\label{suppfigure:IDCDCPnodipAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrDP.pdf}
\caption{Ancestral state estimation using the maximum a posteriori for each node of the M1, D/P ploidy model. } % XXX
\label{suppfigure:DPnodipasr}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrDPAB.pdf}
\caption{Ancestral state estimation using the maximum a posteriori for each node of the M4, D/P+A/B asym model.} % XXX
\label{suppfigure:DPnodipABasr}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrIC.pdf}
\caption{Ancestral state estimation using the maximum a posteriori for each node of the M1, I/C breeding system model.} % XXX
\label{suppfigure:ICasr}
\end{suppfigure}

>>>>

Using the marginal likelihood values, we calculated Bayes factors to answer five key biological and methodological questions:
\begin{enumerate}
\item Are diversification patterns only determined by hidden states and not the traits of interest?---Comparison of character independent models against hidden state (\cref{table:bayesfactors,table:M11M15,supptable:M6M10,supptable:M16M20,supptable:M21M25}).
\item Are hidden states necessary to explain diversification rate heterogeneity?---Comparison of simple models against hidden state models (\cref{supptable:testaddhidden}).
\item Does a second focal trait add information about the diversification process?---Comparison of lumped models against IC/CD/CP models (\cref{figure:lumped,table:lumped,suppfigure:lumpedDP,suppfigure:lumpedIC}).
\item Are conclusions robust to assumptions about hidden state transitions?---Comparison amongst hidden states models with equal hidden rates and asymmetrical rates (\cref{supptable:asymmetry,suppfigure:asymmetric}).
\item Is there evidence for diploidization?---Comparison amongst log-scalemodels with and without diploidization (\cref{supptable:testdiploidization,suppfigure:alldip}).
\end{enumerate}

Each model comparison is reported with a Bayes factor on the natural log-scale: the comparison between models $M_0$ and $M_1$ is $K=ln(BF(M_1,\ M_0)) = \ln[ P(\mathbf{X} | M_1) - P(\mathbf{X} | M_0)]$.
There is `strong evidence' for $M_1$ when this value is more than 10, moderate support if the value is more than 1, and no evidence if the value is between -1 and 1.
If the value of $K$ is negative the evidence goes towards $M_0$ \citep{kass1995}.

@@

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M2    & M3     & M4    & M5     & Evidence                                                                                     \\ \hline
M1. D/P              & -1283.76                                                          & 59.90 & 49.23  & 60.48 & 58.82  & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M1\end{tabular}            \\ \hline
\textbf{M2. CID D/P} & \textbf{-1223.86}                                                 &       & -10.66 & 0.579 & -1.079 & \begin{tabular}[c]{@{}l@{}}Strong preference for \\ M2 over M1 and M3\end{tabular}              \\ \hline
M3. D/P+A/B          & -1234.52                                                          &       &        & 11.24 & 9.58   & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}   \\ \hline
\textbf{M4. D/P+A/B asym}     & \textbf{-1223.28}                                                          &       &        &       & -1.658 & \begin{tabular}[c]{@{}l@{}}Moderate evidence for\\ only asymmetric hidden rates\end{tabular} \\\hline
M5. D/P+A/B all asym & -1224.93                                                          &       &        &       &        &          \\ \hline                                                                                   
\end{tabular}
\caption{Bayes factors for ploidy only models without diplodization in log-scale.  Numbers smaller than -1 indicate moderate preference for the model listed in the row, and values larger than 1 indicate moderate preference for the model listed in the respective column .  Conventional threshold for `strong' preference is an absolute value larger than 10.  The character independent model (M2, bold) is strongly preferred over the ploidy only model (M1) or a hidden state model with symmetric rates (M3). Moderate support exists for the model with ploidy and asymmetric hidden states (M4, bold) over the rest of the ploidy only models.}
\label{table:bayesfactors}
\end{table}

% B: M111->M11
\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                      & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M12   & M13   & M14   & M15   & Evidence                                                                                       \\ \hline
M11. I/C                   & -1309.07                                                          & 41.13 & 38.59 & 61.34 & 61.40 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M11\end{tabular}            \\ \hline
M12. CID I/C               & -1267.93                                                          &       & -2.53 & 20.21 & 20.37 & \begin{tabular}[c]{@{}l@{}}Models with asymmetric rates\\ are preferred over  M12\end{tabular} \\ \hline
M13. I/C+A/B               & -1270.47                                                          &       &       & 22.75 & 22.80 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}   \\ \hline
\textbf{M14. I/C+A/B asym} & \textbf{-1247.72}                                                 &       &       &       & 0.05 & No evidence                                                                                    \\ \hline
\textbf{M15. I/C+A/B all asym }     & \textbf{ -1247.66}                                                          &       &       &       &       &       \\ \hline                                                                                        
\end{tabular}
\caption{Bayes factors for breeding system only models in log-scale.  Numbers smaller than -1 indicate moderate preference for the model listed on the row, and values larger than 1 indicate moderate preference for the model in the respective column.  Conventional threshold for `strong' preference is an absolute value larger than 10. Moderate to strong preference exist for models M14 and M15 which include a hidden states with asymmetrical rates.}
\label{table:M11M15}
\end{table}

@@

\begin{table}[]
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|c|c|c|c|}
\hline
Model                       & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & Comparison  & K=ln(BF($M_{i}$,$M_{ii}$)) & \begin{tabular}[c]{@{}l@{}}Preferred\\ Model (Evidence)\end{tabular} \\ \hline
M26. Lumped D/P             & -1463.22                                                          & M26 vs. M16 & 4.10            & M16 (Moderate)                                                       \\
\textbf{M16. ID/CD/CP}      & \textbf{-1459.11}                                                 &             &                 &                                                                      \\ \hline
M27. Lumped D/P+A/B         & -1417.67                                                          & M27 vs. M23 & 3.678           & M23 (Moderate)                                                       \\
\textbf{M23. ID/CD/CP +A/B} & \textbf{-1414.00}                                                 &             &                 &                                                                      \\ \hline
M28. Lumped I/C             & -1458.41                                                          & M28 vs. M16 & -0.69           & No evidence                                                          \\
M16. ID/CD/CP      & \textbf{-1459.11}                                                 &             &                 &                                                                      \\ \hline
M29. Lumped I/C+ A/B        & -1416.60                                                          & M29 vs. M23 & 2.60            & M23 (Moderate)                                                       \\
\textbf{M23. IC/CD/CP+A/B}  & \textbf{-1414.00}                                                 &             &                 &                                                                      \\ \hline
\end{tabular}
\caption{Testing the addition of a focal trait to a binary state model via Bayes factors (log-scale). Numbers smaller than -1 indicate moderate preference for the model in the row, and values larger than 1 indicate moderate preference for the model in the respective column.  Conventional threshold for `strong' preference is an absolute value larger than 10. Three-state models (M16, M23, bold) are moderately preferred over two-state models . Moderate evidence exists towards the inclusion of breeding systems in ploidy models (M16, M23, bold). Moderate to no evidence towards the  inclusion of ploidy in breeding system models is indicated by the comparisons of models M28 \vs M16 and M29 \vs M23 where the difference is the inclusion of ploidy information.}
\label{table:lumped}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{states.pdf}
\caption{
Character states used in the models.
(A) Each species retained on the phylogeny belonged to one of five possible categories, depending on whether ploidy and/or breeding system were known. 
Number of species in each category is indicated; for example, 70 species are self-compatible with unknown ploidy.
Character state abbreviations are: $I$ for self-incompatible, $C$ for self-compatible, $D$ for diploid, $P$ for polyploid, $?$ for unknown.
Because polyploidization breaks this form of self-incompatibility, self-incompatible species with unobserved ploidy ($I?$) are taken to be diploid ($ID$), and polyploid species with unobserved breeding system ($?P$) are taken to be SC ($CP$).
(B) Category groupings into states for each model class.
In the ploidy-only models (M1- M10), states are coded as $D$ \& $P$ when uncertain/consistent with either state; in the breeding system-only models (M11-M15) such states are coded as $C$; in the ploidy and breeding system models (M16-M29), they are coded as $CD$ \& $CP$.
In the hidden-trait models, all species could take on either of two `hidden' character states. %IM: #33 
Two species, \emph{Lycium californicum} and \emph{Solanum bulbocastanum}, are simultaneously $ID$ and $CP$, and by adding them the sample adds to the total of 651 taxa used for analyses.
}\label{figure:stateclassifications}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{alldiversificationasymhidden.pdf} 
\caption{Net diversification rates for SSE models of focal traits with or without hidden state. 
(A) Ploidy only model (M1) showing higher net diversification linked to diploid state $D$ compared to polyploid state $P$.
(B) Ploidy with hidden states model (M4) showing that the net diversification is higher for hidden state $B$ (lighter colors) compared to hidden state $A$ (darker colors) and both diploid and polyploid states within each hidden traits have overlapping net diversification rates.
(C) Breeding system only model (M9) showing higher net diversification linked to self-incompatible $I$ state compared to self-compatible state $C$.
(D) Breeding system with hidden states model (M11) showing diversification differences in both hidden states (light \vs. dark colors) and little to no overlapping in between self-compatible \vs self-compatible states.
(E) Ploidy and breeding system model (M13) showing higher net diversification linked to self-incompatible diploid state $ID$ compared to both self-compatible states despite ploidy level ($CD, CP$).
(F) Ploidy, breeding system, and hidden states model (M16) showing a similar pattern that panel (E) within each hidden state $A$ and $B$. For hidden state $B$ there is a larger overlap of net diversification between states $CD_B$ and $ID_B$.}
\label{figure:netdivall}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{lumped.pdf} %lumped.pdf
\caption{Comparing two and three-state models using lumped models. (A) Ploidy model only (M1) where data enter as binary $D$ and $P$. 
(B) Lumped model for ploidy (M26) where data are the three-state values ($ID,CP,CD$) but results are equivalent to model M1.  
(C) Ploidy and breeding system model (M16) where  data enter as the three-state values. Models M26 and M16 are comparable whereas M1 and M16 are not.
(D) Breeding system only model (M11) where data are entered as binary $I$ and $C$. 
(E) Lumped model for breeding system (M28) where data are the three-state values ($ID,CP,CD$) but results are equivalent to model M11. Model M26 can be compared with model M16 from panel (C).
Model comparisons are done via Bayes factors and results are shown in \cref{table:lumped}}  
\label{figure:lumped}
\end{figure}

@@

@@

\begin{suppfigure}
    \caption{ Twenty-nine models of diversification are proposed for the study of ploidy, breeding systems, and hidden states linked to the process of diversification. We divide the models by the type of focal trait studied (ploidy only, breeding system only, or ploidy and breeding system). The contributions of the focal trait to the diversification process can be measured by comparing the models in each of the columns. That is, the focal trait only models assume that speciation and extinction rates are only linked to the trait itself, the hidden trait only models assume that the diversification rates are  linked to unknown factors but not the trait of interest, and the focal trait with hidden trait models assume that both the focal trait and unknown factors are contributing to diversification.}
    \label{fig:allmodels}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseDPnodipposteriordist.pdf}
\caption{Posterior distributions for each of the parameters in the ploidy only model (M1). Red color represents diploid state $D$ and blue color represents polyploid state $P$.  (A)Speciation rates. (B) Extinction rates. (C) Net diversification rates (speciation minus extinction from panels A and B). (D) Relative extinction rates (extinction divided by speciation from panels A and B). (E) Polyploidization rate ($\rho$).} % XXX
\label{suppfigure:DPnodip}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseDPnodipasymposteriordist.pdf}
\caption{Posterior distributions for each of the parameters in the ploidy and hidden trait model (M4). Red color represents diploid state $D$ and blue color represents polyploid state $P$. Dark colors represent hidden state $A$ and light colors hidden state $B$.  (A) Speciation rates. (B) Extinction rates. (C) Net diversification rates (speciation minus extinction from panels A and B). (D) Relative extinction rates (extinction divided by speciation from panels A and B). (E) Polyploidization rate ($\rho$). (F) Transition rates between hidden states ( $\alpha$ and $\beta$).} % XXX
\label{suppfigure:DPnodipAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseSIposteriordist.pdf}
\caption{Posterior distributions for each of the parameters in the breeding system only model (M11). Green color represents self-incompatible state $I$ and purple color represents self-compatible state $C$.  (A) Speciation rates. (B) Extinction rates. (C) Net diversification rates (speciation minus extinction from panels A and B). (D) Relative extinction rates (extinction divided by speciation from panels A and B). (E) Self-incompatible to self-compatible transition rate ($q_IC$).} % XXX
\label{suppfigure:IC}
\end{suppfigure}
